### 2017-06-01 sheets/basis-5/sheet-basis-5.tex
fixed one exercise

\textbf{Corollary}: Let $G: \B \rightarrow \A$ be a functor. Then G has a left adjoint if and only if for each $A \in \A$, the category ($A \Rightarrow G$) has an initial object.\\

\begin{exercise}
State and prove the dual of this corollary.
\end{exercise}

\begin{exercise}
\begin{enumerate}
\item Give an example of an adjunction that is not an equivalence.
\item Let ($F, G, \eta, \epsilon$) be an equivalence of categories. Prove that F is left adjoint to G.
\end{enumerate}
\end{exercise}

>>>>

\textbf{Fact}: Let $G: \B \rightarrow \A$ be a functor. Then G has a left adjoint if and only if for each $A \in \A$, the category ($A \Rightarrow G$) has an initial object.\\

\begin{exercise}
State and prove the dual of the above fact.
\end{exercise}

\begin{exercise}
  Recall Definition 1.3.15 of the script, which states that an equivalence of categories $\A$ and $\B$ consists of two functors $F$ and $G$ and two natural isomorphisms $\eta$ and $\epsilon$ which relate their compositions to the respective identity functors.
\begin{enumerate}
\item Give an example of an adjunction that is not an equivalence.
\item Let ($F, G, \eta, \epsilon$) be an equivalence of categories. Prove that F is left adjoint to G.
\end{enumerate}
\end{exercise}
